A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-05-14 src/paper.tex
Updated introduction with the revision from Prof. Vicente

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV it is possible to develop high level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channel and volume.

The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV e.g., change channel and volume. In explicit interactions, viewers contribute by actively evaluating, commenting or sharing their opinion about a given content. Both kinds of interaction are important for applications that rely on audience generated data.

Considering the interactions of millions of viewers, the captured data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}. For example, the CPs can obtain the user ratings given to TV programs, amount of viewers and user profiles. By using proper machine learning algorithms, CPs can infer viewer tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}. However, identifying viewers and capturing their individual interactions is still a challenging activity in the traditional TV environment, which consists of the TV and viewers interacting through a remote control (RC).

The conventional RC is the input device that viewers typically use to interact with the TV. However, the RC presents two notable problems for capturing interactions from viewers: (1) to automatically identify the viewers that are in the TV environment in order to contextualize the interaction; and (2) to individually capture interactions from the viewer in charge of the RC. Thus, considering a scenario with the traditional TV environment and a conventional TV, all interactions are assigned to the whole group of viewers (e.g., a family), rather than to the viewer in charge of the RC. As a result, the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of others.

As a potential alternative to handle the limitations of the RC for capturing interactions from viewers, the proliferation of personal mobile devices has changed the people behavior towards audiovisual content consumption in interactive TV environments. Nowadays, viewers rarely just sit passively and watch TV. In many situations, they use their personal devices as a secondary screen to perform activities related to TV watching, which end up enriching and immersing the user into the TV experience.

>>>>

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV it is possible to develop high level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume.

The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV e.g., changing channels. In explicit interactions, viewers contribute by actively evaluating, commenting or sharing their opinion about a given content. Both kinds of interaction are important for applications that rely on audience generated data.

Considering the interactions of millions of viewers, the captured data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}. For example, the CPs can obtain the user ratings given to TV programs, amount of viewers, and user profiles. By using proper machine learning algorithms, CPs can infer viewers' tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}. However, identifying viewers and capturing their individual interactions is still a challenging activity in the traditional TV environment, which consists of the TV and viewers interacting through a remote control (RC).

The conventional RC presents two notable problems for capturing interactions from viewers: (1) to automatically identify the viewers that are in the TV environment in order to contextualize the interaction; and (2) to individually capture interactions from the viewer in charge of the RC. Thus, considering a scenario with the traditional TV environment and a conventional TV, all interactions are assigned to the whole group of viewers (e.g., a family), rather than to the viewer in charge of the RC. As a result, the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

As a potential alternative to handle the limitations of the RC, the proliferation of personal mobile devices has changed the people behavior towards audiovisual content consumption in interactive TV environments. Nowadays, viewers rarely just sit passively and watch TV. In many situations, they use their personal devices as a secondary screen to perform activities related to TV watching, which end up enriching and immersing the user into the TV experience.
